\section{Introduction}
\subsection{Project Start Meeting (Kick-Off)}

\subsection{Project Start Meeting (Kick-Off)}
\subsection{Project Management Methodology}
\subsubsection{Introduction to Scrum}
\subsubsection{Adaptation to Our Project}
\subsubsection{Using JIRA for Task Management}
\subsection{Software Development}
\subsubsection{Goals for Software Development}
\subsubsection {Programming Languages and Frameworks}

Python: Python was the primary programming language used for the development of the project. It was utilized for data manipulation, analysis, and visualization. The modules and libraries used in Python include:

\begin{itemize}
\item Data: This module is responsible for handling data-related tasks.
\item numpy: A library for numerical operations and computations.
\item pandas: A library for data manipulation and analysis.
\item matplotlib: A library for data visualization.
\item json: A library for handling JSON data.
\item networkx: A library for graph-based operations.
\item Markdown: Markdown was used for generating documentation in a readable and formatted manner.
\item pdfkit: pdfkit was employed for converting HTML content to PDF format.
\item HtmlConverter: HtmlConverter is a module used for converting HTML content to other formats.
\item SpecialDates: This class provides functionality related to special dates.
\item OneExamPerDay: This class ensures that only one exam per day is scheduled.
\item Scoring: Scoring is a module responsible for calculating scores based on certain criteria.
\item Output: The Output class is used for generating output in various formats.
\item RoomCapacity: This class handles calculations and checks related to room capacity.
\item RoomDistance: RoomDistance class is responsible for calculating distances between different rooms.
\item BigExamsEarly: This class prioritizes scheduling big exams early.
\item SpecialProfessors: SpecialProfessors class is used for handling professors with special requirements.
\item OneDayGap: OneDayGap class ensures that there is at least one day gap between exams.
\item csv: The csv module is used for reading and writing CSV files.
\item random: The random module is used for generating random values.
\end{itemize}

These programming languages, frameworks, and classes were utilized to implement various functionalities and achieve the desired goals of the project.
\subsubsection{Development Environment}
\subsubsection{Maven Project Template}
\subsubsection{Using Bitbucket for Source Code Management}
\subsection{Documentation}
\subsubsection{Goals for Documentation}
\subsubsection{Target Audience and Language Used}
\subsubsection{Format of Documentation}
\subsubsection{Structure of Documentation}
\subsubsection{Guidelines for the Content of Each Chapter}
\subsubsection{Authorship Attribution}
\subsection{Presentation}
\subsection{Regular Meetings Throughout the Semester}
\subsection{Dealing with Issues}
\subsection{Semester Timeline}


